\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref} 
\thispagestyle{empty}
\addtolength{\oddsidemargin}{-.875in}
	\addtolength{\evensidemargin}{-.875in}
	\addtolength{\textwidth}{1.75in}

	\addtolength{\topmargin}{-1.25in}
	\addtolength{\textheight}{1.75in}
\title{Resume}
\author{Areeba Khan}
\date{September 2021}

\begin{document}
%
% Header of Page %
%
\begin{center}
    \section*{\LARGE{Areeba Khan}}\vspace{-0.75em}
    \small +1 314-256-9928\qquad \href{mailto:khan6@stolaf.edu}{\underline{khan6@stolaf.edu}} \qquad \href{https://linkedin.com/in/areebok}{\raisebox{-0.2\height}\ linkedin.com/in/\underline{areebok}}   \qquad \href{https://github.com/aReebok}{\raisebox{-0.2\height}\ github.com/\underline{aReebok}}
    \vspace{-1em}
\end{center}
%
% end of header%
%

\section*{\large\textbf{Education}}\vspace{-0.5em}\hline\vspace{0.5em}
\small \textbf{St. Olaf College}, Northfield, MN \hfill \small\textbf{Expected May 2023}

\textit{Bachelor of Arts in Computer Science and Neuroscience Concentration} \hfill \small GPA: 3.73
\vspace{0.35em}

\noindent
\small \textbf{Carleton College}, Northfield, MN \hfill \textbf{\small2020-2021}

\textit{CS Courses inter-registration through St. Olaf College}
\vspace{-1em}
% \section*{\normalsize{Courses:} } \vspace{-1em} 
\section*{\large{Professional/Volunteering Experiences}}\vspace{-0.5em}\hline\vspace{0.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% CLUSTER MGMT 
%%%
% \normalsize{}\textbf{Cluster Manager} at St. Olaf College \hfill \small\textbf{Starting Fall 2021} \vspace{-0.6em}
% \begin{itemize}
% \item \normalsize{Completed cluster management training/researched Kubernetes clusters beyond base training}.  \vspace{-0.6em}
% \item \normalsize{Work on projects assigned to our team to complete them by given deadlines}.  \vspace{-0.6em}
% \item \normalsize{Attend weekly meetings and work at least 5 hours per week towards cluster management}.  \vspace{0em}
% \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% CODE IN PLACE 
%%%
\noindent
\normalsize{}\textbf{Code in Place} through Stanford University \hfill \small\textbf{2020, 2021} \vspace{-0.6em}
\begin{itemize}
\item \normalsize{Section Leader (Summer 2020, 2021)}.  \vspace{-0.6em}
    \begin{itemize}
        \item Prepared and taught a weekly section of 10-12 diverse college students to supplement professors’ lectures in a 5-week introductory online Python programming course based on material from the first half of Stanford’s introductory programming course, CS106A.\vspace{-0.6em}
    \end{itemize}
\item \normalsize{Section Leader Mentor (Summer 2021)}.  \vspace{-0.6em}
    \begin{itemize}
        \item Led two 3-hour-long training sessions for 18-20 new volunteer section leaders, discussing remote CS teaching methods, suggestions on maintaining personal and the student’s privacy, and social responsibilities.\vspace{-0.6em}
    \end{itemize} \vspace{0em}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% MICROSOFT TEALS
%%%
\noindent
\normalsize{}\textbf{Microsoft TEALS} Remote TA and Teacher at Oaks High School \hfill \textbf{(Academic year 2021-22)} \vspace{-0.6em}
\begin{itemize}
    \item Attending 2 hours as a teacher assistant and teaching regularly on Fridays.     \vspace{-0.6em}
    \item Attending weekly meetings with a team of 3 other TEALS volunteers to discuss student feedback/potential issues and fixes.     \vspace{-0.6em}
    \item Contributing to writing auto-graders in Python for homework assignments and projects for current and future TEALS curriculum use.  \vspace{-0.6em}
\end{itemize}
\vspace{-1.5em}
\section*{\large{Projects}}\vspace{-0.5em}\hline\vspace{0.5em}
\noindent
\textbf{Scheme Interpreter in C Language} with Molly Kammann at Carleton College \hfill \textbf{2021}

\noindent
\textbf{Multi-threading in Scheme} and informal time analysis presentation/report \hfill

\noindent
\textbf{Data Displaying Program in Java, } using various data structures and \hfill \textbf{2020}

\noindent
\textbf{Adventure Game in C++, React Native} in Software Development \hfill \textbf{2019}

\noindent
\textbf{Mosaic-fy Photo Application in Python} using Matplotlib and GUI \hfill \textbf{}
% \textbf{Parallel Programming and Time Analysis in Scheme} - rewrite Drug Exemplar in Scheme \href \textbf{Spring 2021}
\vspace{0.5em}


\hline\vspace{0.5em}
\noindent
\textbf{Tools/skills}: C/C++, Python, Scheme, Java, \LaTeX, HTML, CSS, JS, ARM Assembly, R, Bash, GitHub, VS Code, Linux, Kubernetes, AWS, mentoring.\vspace{0.2em}

\noindent
\textbf{Hobbies}: Computer/lab equipment repair at WashU, project blogging, photography.
\vspace{0.2em}

\noindent
\textbf{Languages}: English, Hindi, limited proficiency in Spanish and self-studying Korean
\vspace{-1em}

\section*{\large{Leadership/Extracurricular}}\vspace{-0.5em}\hline\vspace{0.6em}

\begin{itemize}
    \item \textbf{Linux Ladies} board member and financial Manager \hfill 2021-present\vspace{-0.6em}
    \begin{itemize}
        \item \textit{leading summer program in building personal website with basics of HTML/CSS/JS}. \vspace{-0.6em}
    \end{itemize}
    \item \textbf{Volunteer Network} First-year Representative\hfill 2019-2020\vspace{-0.6em}
    \item \textbf{First Robotics} High School Coding Team Co-Captain\hfill 2018-2019\vspace{-0.6em}
    \item \textbf{Clayton Connect Tutoring Club} President \hfill \vspace{-0.6em}

    
\end{itemize}

\end{document}